% Emacs, this is -*-latex-*-

% Free-riding Control at the Splitter

\label{sec:free_riding_control}

Monitor peers (which are trusted peers) complain to their splitter
with a $[\mathtt{lost}~\text{lost\_chunk\_number}]$ for each lost
chunk that they detect. The splitter only considers these type of
messages if they come from a monitor. FCS (see Sec. \ref{sec:FCS}) is
used to control free-riders at peers.

The splitter remembers which chunk, of a list of the last $B'$
transmitted chunks, was sent to each \leo{origin} peer of the team. \st{Notice that, in
order to remember the chunk that was sent to each peer in each round,} {\color{red} Por qué no vale esto?}
It must be hold that $B'\ge N$. \note{See
  \href{https://github.com/P2PSP/simulator/blob/f0c73be1817e7d3b816cc61cd2c8e59b17f9a0e6/src/core/splitter_dbs.py\#L296}{$\text{destination\_of\_chunk}[]$
    in \texttt{splitter\_dbs.py}}.}

The splitter counts of lost chunks for each peer of the team. The
corresponding counter is incremented for each lost chunk reported and
all counters are decremented at the end of each round (clipping at
zero). When a counter is greater than a threshold, the corresponding
peer is deleted from the list of peers. Controlling the threshold,
this procedure allows to reject from the team those peers that are not
able to forward the chunks received from the splitter with more of
less belligerence.

%Notice that $L$ will
%tend to be proportional to the number $M$ of monitors, especially if
%those cases where $P_o$ is a gone peer that was unable to transmit the
%$[\mathtt{goodbye}]$ messages.

\begin{notex}
This last functionality has not been implemented, at least, as it has
been explained here. The forget() thread is controlled by a timer, not
by a counter of rounds.
\end{notex}

%Peers also control that at least one chunk is received from a neighbor
%in each round.\footnote{Peers recognize that a new round has started
%  when a new chunk is received from the splitter.} If happens that a
%peer $P_x$ does not receives a chunk from peer $P_y$ between $D^*$
%consecutive rounds, $P_x$ removes $P_y$ of its forwaring table.
